Prefetching SPARQL query cacher

### 2016-07-29 dissertation/cache-proxy.tex
elaborate the costs

Next, we detail the cost of a join where one or more children in the
tree is a remote SPARQL plan. It is usually not wanted to execute
several remote queries, it is assumed that the number of HTTP requests
should be small, and that plans where the joins have been rotated and
coalesced by \pmodule{AtteanX::API::JoinRotatingPlanner} should be
less expensive. Therefore, such plans should be penalised, but by how
much depends on the type plans. Conventionally, for a nested loop join
plan, we multiply the cost of the subplans, increment the resulting
cost by one if the right hand plan is more expensive than the left
hand plan, and multiply by a factor of 10 if there are no shared
variables, to mildly penalise Cartesian joins. If the plan is a hash
join the difference is that we add rather than multiply the cost of
the of the subplans, and multiply by a factor of 100 rather than 10 so
that if it is necessary to evaluate a Cartesian join, it is more
likely done using a nested loop join. Then, the resulting cost is
multiplied by the number of remote SPARQL Basic Graph Patterns in the
tree and the factor 1.2, and floored to the nearest integer.

>>>>

Next, we detail the cost of a join where one or more children in the
tree is a remote SPARQL plan. It is usually not wanted to execute
several remote queries, it is assumed that the number of HTTP requests
should be small, and that plans where the joins have been rotated and
coalesced by \pmodule{AtteanX::API::JoinRotatingPlanner} should be
less expensive. Therefore, such plans should be penalised, but by how
much depends on the type plans. Conventionally, for a nested loop join
plan, the we first assign 
\begin{equation}\label{eq:cnl}
T_{A \bowtie_{nl} B} = 10 ((1 + C_A) C_B ) ,
\end{equation}
where $A$ and $B$ signifies the left and right subplans, and $C_A$ and
$C_B$ their respective cost estimates (which is originates from the
other heuristics in this section).  Following the default
implementation in Attean, we multiply the cost in Eq.~(\ref{eq:cnl})
by a factor of 10 if there are no shared variables, to mildly penalise
Cartesian joins.

If the plan is a hash join the, we continue to follow the example of
the Attean implementation and set
\begin{equation}\label{eq:ch}
T_{A \bowtie_{h} B} = 10 ((1 + C_A) + C_B ) .
\end{equation}
Further, if there are no shared variables, the cost of
Eq.~(\ref{eq:ch}) is multiplied by a factor of 100 rather than 10 so
that if it is necessary to evaluate a Cartesian join, it is more
likely done using a nested loop join.

Then, to make local joins somewhat more expensive than similar BGPs\todo{check},
for both these join types, we designate the cost of joins to be
\begin{equation}\label{eq:cjoins}
C_{A \bowtie_* B} = \floor{ 1.2 n_{rs} T_{A \bowtie_{*} B} } ,
\end{equation}
where the asterisk denotes either $nl$ for nested loop or $h$ for hash
join, respectively, and $n_{rs}$ is the number of remote SPARQL Basic
Graph Patterns in the tree.
